---
title: "Journal"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```




So, let's say you are learning how to make a histogram in R. For example, maybe you want to sample 100 numbers from a normal distribution with mean = 0, and standard deviation =1, and then you want to plot a histogram. You can do this right here by using an r code block, like this:

```{r}
samples <- rnorm(100, mean=0, sd=1)
hist(samples)
```



# Problem 1

Do simple math with numbers, addition, subtraction, multiplication, division

```{r}
1+5
2*5.5
15/333
(1+6+4)/5

```



# Problem 2

Put numbers into variables, do simple math on the variables

```{r}
a<-1
b<-2
a+b

d<-c(1,2,3)
e<-c(5,6,7)
d+e
d*e
d/e

```



# Problem 3

Write code that will place the numbers 1 to 100 separately into a variable using for loop. Then, again using the seq function.

```{r}
# for loop solution
# i becomes the number 1 to 100 at each step of the loop


a <- length(100) # make empty variable, set length to 100
for (i in 1:100){
  a[i] <-i #assigns the number in i, to the ith index of a
}

print(a)

# for loop solution #2

a<-c() #create empty variable using combine command
for (i in 1:100){
  a<-c(a,i) # keeps combining a with itself and the new number in i
}
print(a)

# seq solution
a <- seq(1,100,1) # look up help for seq using ?seq() in console
print(a)

```



# Problem 4 Replace this with problem 4

And keep going. Try to solve the problems with different scripts that provide the same solution. Good luck, Happy coding.



# Program 5 Summing

```{r}
#RANGE 1->100
sum(1:100)

```
##Using a Loop - followed a YouTube  tutorial
```{r}
tot = 0 
calc <- 1 

while(calc <= 5)
{

  tot = tot + calc 
  
  calc = calc + 1
  
}
print(paste("The sum is", tot))
```

```{r}
for (i in 1:5){
  print(i^2)
  }
```  

### Notes: So i is first 1, it is squared. then i is 2 and it is squared, etc. So what if I wanted to add all these squares in the loop? Average? 

```{r}
Storage<-numeric(5)
for (i in 1:5){
  print(i^2)
Storage[i]<-i^2
  }
Storage
sum(Storage)
mean(Storage)
```



#Problem 6: Sum Any Two Integers (Work in progress)

